
# Read data

```{r}
if(!file.exists("repdata-data-activity.zip")) {
  temp <- tempfile()
  download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temp)
  unzip(temp)
  unlink(temp)
}
```

# See data

```{r}
activity <- read.csv("activity.csv")
head(activity)
names(activity)
```

# Transform data

```{r}
activity$date <- as.Date(activity$date, "%Y-%m-%d")
Totalsteps <- aggregate(steps ~ date, data=activity, sum, na.rm=TRUE)
head(Totalsteps)
```

# Make a histogram of the total number of steps

```{r, echo=FALSE}
hist(Totalsteps$steps, xlab= "day", col= "blue", main="Total Number of Steps by Day") 
```

# Mean and Median of steps taken per day: Calculate and report the mean and median of the total number of step

```{r}
mean(Totalsteps$steps)
median(Totalsteps$steps)
```

# Average daily activity pattern

```{r}
interval <- aggregate (steps~interval, data=activity, sum) 
```

```{r, echo=FALSE}
plot(steps_interval, type="l", xlab="interval", ylab="steps", col="red", main="Average Daily Activity Pattern")
```

```{r}
maximum_number_steps <- steps_interval[which.max(steps_interval$steps),1]
```

# Imputing missing values: Calculate and report the total number of missing values

```{r}
missing_values <- sum(is.na(activity$steps))
```

# Devise a strategy for filling in all of the missing values


```{r}
Fill_missing_values <- aggregate (steps~interval, data=activity, FUN=mean)
Fill_NA <- c(Fill_missing_values, steps~interval)
```

# Create a new dataset 

```{r}
dataset1 <- activity
dataset2 <- Fill_NA
```


# Make a histogram of the total number of steps taken each day and Calculate 

```{r}
Totalsteps <- aggregate(steps~date, data=dataset1, sum, na.rm=TRUE)
```

```{r, echo=FALSE}
hist(Totalsteps$steps, xlab="day", col="blue", main="Total Number of Steps")
```


# Report the mean and median total number of steps taken per day

```{r}
mean (Totalsteps$steps)
median(Totalsteps$steps)
```


# Differences in activity patterns between weekdays and weekends

```{r}
head(activity)
library(lattice)
activity$date<-as.Date(activity$date,format = '%Y-%m-%d')
activity$day <- ifelse(weekdays(activity$date) %in% c("Saturday", "Sunday"),'weekend','weekday')
head(activity$day)
stepsDaytype<-aggregate(steps~ interval+day,activity,FUN="mean")
head(stepsDaytype)
names(stepsDaytype) <- c("interval", "daylevel", "steps")
```


```{r, echo=FALSE}
xyplot(steps ~ interval | daylevel, stepsDaytype, layout = c(1, 2), type = "l", col="red", xlab="interval", ylab="steps", main="Activity Patterns between Weekdays and Weekend")
```
